target_offtarget

### 2025-01-22 manuscript_figures.Rmd
Updating supp figures

@@

### Figure S6
```{r}

@@

#### ***Final plot***
```{r}
ggsave("figures/manuscript_figure_2025/PDF/Figure_S4.pdf",
       width=9,
       height=8)

ggsave("figures/manuscript_figure_2025/PNG/Figure_S4.png",
       width=9,
       height=8)
```

@@

### Figure S7
```{r}

persite_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  filter(virus == "Zika_virus") |>
  ggplot(aes(x = site, y = coverage, fill = Background)) +
  geom_col() +
  facet_wrap(Viral.load ~ Sample_id) +
  ylab("log10(Coverage)") +
  ggtitle("Zika virus (deduplicated)") +
  guides(fill = guide_legend(title = "Background")) +
  theme_bw() +
  scale_y_log10() +
  scale_fill_manual(values = cols2, labels = c("P1", "P2"))

#ggsave("figures/manuscript_figures_pdf/FigureS6.pdf",width=10,height=8)

@@

### Figure S8
```{r}
persite_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  filter(virus == "Human_adenovirus_40") |>
  ggplot(aes(x = site, y = coverage, fill = Background)) +
  geom_col() +
  facet_wrap(Viral.load ~ Sample_id) +
  ylab("log10(Coverage)") +
  ggtitle("Human Adenovirus (deduplicated)") +
  guides(fill = guide_legend(title = "Background")) +
  theme_bw() +
  scale_y_log10() +
  scale_fill_manual(values = cols2, labels = c("P1", "P2"))

#ggsave("figures/manuscript_figures_pdf/FigureS7.pdf",width=20,height=18)
```

@@

### Figure S9
```{r}
persite_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  filter(virus == "Human_betaherpesvirus") |>
  ggplot(aes(x = site, y = coverage, fill = Background)) +
  geom_polygon() +
  facet_wrap(Viral.load ~ Sample_id) +
  ylab("log10(Coverage)") +
  ggtitle("Human Betaherpesvirus (deduplicated)") +
  guides(fill = guide_legend(title = "Background")) +
  theme_bw() +
  scale_y_log10() +
  scale_fill_manual(values = cols2, labels = c("P1", "P2"))

#ggsave("figures/compare_spike_ins_atcc/HBHV_coverage_test.pdf",width=20,height=18)
```

@@

### Figure S10
```{r}
#have to do these differently due to segmentation

FLU_ME1 <- persite_norm |>
  filter(virus == "Influenza_B_virus") |>
  filter(type == "dedup_TE") |>
  filter(Background == "p2") |>
  ggplot(aes(
    x = site,
    y = coverage,
    fill = as.character(Viral.load)
  )) +
  geom_col() +
  facet_grid(seg ~ Sample_id) +
  ylab("log10(Coverage)") +
  ggtitle("Influenza B virus (Background 1 deduplicated)") +
  guides(fill = guide_legend(title = "Viral load")) +
  theme_bw() +
  scale_y_log10() +
  scale_fill_manual(values = cols4,
                    labels = c("1e+02", "1e+03", "1e+05"))

FLU_ME2 <- persite_norm |>
  filter(virus == "Influenza_B_virus") |>
  filter(type == "dedup_TE") |>
  filter(Background == "p8") |>
  ggplot(aes(
    x = site,
    y = coverage,
    fill = as.character(Viral.load)
  )) +
  geom_col() +
  facet_grid(seg ~ Sample_id) +
  ylab("log10(Coverage)") +
  ggtitle("Influenza B virus (Background 2 deduplicated)") +
  guides(fill = guide_legend(title = "Viral load")) +
  theme_bw() +
  scale_y_log10() +
  scale_fill_manual(values = cols4,
                    labels = c("1e+02", "1e+03", "1e+05"))

@@

#ggsave("figures/manuscript_figures_pdf/FigureS9.pdf",width=20,height=18)
```

@@

### Figure S11
```{r}

REO_ME1 <- persite_norm |>
filter(virus == "Mammalian_orthoreovirus3") |>
filter(type == "dedup_TE") |>
filter(Background == "p2") |>
ggplot(aes(
x = site,
y = coverage,
fill = as.character(Viral.load)
)) +
geom_col() +
facet_grid(seg ~ Sample_id) +
ylab("log10(Coverage)") +
ggtitle("Mammalian orthoreovirus 3 (Background 1 deduplicated)") +
guides(fill = guide_legend(title = "Viral load")) +
theme_bw() +
scale_y_log10() +
scale_fill_manual(values = cols4,
labels = c("1e+02", "1e+03", "1e+05"))

REO_ME2 <- persite_norm |>
filter(virus == "Mammalian_orthoreovirus3") |>
filter(type == "dedup_TE") |>
filter(Background == "p8") |>
ggplot(aes(
x = site,
y = coverage,
fill = as.character(Viral.load)
)) +
geom_col() +
facet_grid(seg ~ Sample_id) +
ylab("log10(Coverage)") +
ggtitle("Mammalian orthoreovirus 3 (Background 2 deduplicated)") +
guides(fill = guide_legend(title = "Viral load")) +
theme_bw() +
scale_y_log10() +
scale_fill_manual(values = cols4,
labels = c("1e+02", "1e+03", "1e+05"))

@@

#ggsave("figures/manuscript_figures_pdf/FigureS10.pdf",width=20,height=18)

@@

>>>>

ggsave("figures/manuscript_figure_2025/PNG/Figure_S3.png", 
       width = 8,
       height = 8)

@@

### Figure S4
```{r}

@@

#### ***Final plot***
```{r}
ggsave("figures/manuscript_figure_2025/PDF/Figure_S4.pdf",
       width=15,
       height=10)

ggsave("figures/manuscript_figure_2025/PNG/Figure_S4.png",
       width=15,
       height=10)
```

@@

### Figure S5
```{r, warning=FALSE, message=FALSE, echo=FALSE}

persite_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  filter(virus == "Zika_virus") |>
  rename(Viral.load = `Viral load`) |>
  ggplot(aes(x = site, y = coverage, fill = Background)) +
  geom_col() +
  facet_wrap(Viral.load ~ Sample_id, label = label_parsed) +
  ylab("Coverage") +
  ggtitle("Zika virus (deduplicated)") +
  guides(fill = guide_legend(title = "Background")) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10() +
  scale_fill_manual(values = cols2, labels = c("P1", "P2"))

####***Final plot***
```{r}

ggsave("figures/manuscript_figure_2025/PDF/Figure_S5.pdf",
       width=15,
       height=10)

ggsave("figures/manuscript_figure_2025/PNG/Figure_S5.png",
       width=15,
       height=10)

@@

### Figure S6
```{r, warning=FALSE, message=FALSE, echo=FALSE}

persite_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  filter(virus == "Human_adenovirus_40") |>
  rename(Viral.load = `Viral load`) |>
  ggplot(aes(x = site, y = coverage, fill = Background)) +
  geom_col() +
  facet_wrap(Viral.load ~ Sample_id, label = label_parsed) +
  ylab("Coverage") +
  ggtitle("Human Adenovirus (deduplicated)") +
  guides(fill = guide_legend(title = "Background")) +
 theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10() +
  scale_fill_manual(values = cols2, labels = c("P1", "P2"))

####***Final plot***
```{r}

ggsave("figures/manuscript_figure_2025/PDF/Figure_S6.pdf",
       width=15,
       height=10)

ggsave("figures/manuscript_figure_2025/PNG/Figure_S6.png",
       width=15,
       height=10)

@@

### Figure S7
```{r}
HBV <- 
persite_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  filter(virus == "Human_betaherpesvirus") |>
  rename(Viral.load = `Viral load`) |>
  ggplot(aes(x = site, y = coverage, fill = Background)) +
  geom_col() +
  facet_wrap(Viral.load ~ Sample_id, label = label_parsed) +
  ylab("Coverage") +
  ggtitle("Human Betaherpesvirus (deduplicated)") +
  guides(fill = guide_legend(title = "Background")) +
 theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10() +
  scale_fill_manual(values = cols2, labels = c("P1", "P2"))

####***Final plot***
```{r}

ggsave(plot = HBV, file="figures/manuscript_figure_2025/PDF/Figure_S7.pdf",
       width=15,
       height=10,
       dpi = 600)

ggsave(plot = HBV, file="figures/manuscript_figure_2025/PNG/Figure_S7.png",
       width=15,
       height=10)

@@

### Figure S8
```{r}
#have to do these differently due to segmentation

FLU_ME1 <- persite_norm |>
  filter(virus == "Influenza_B_virus") |>
  filter(type == "dedup_TE") |>
  filter(Background == "p2") |>
  rename(Viral.load = `Viral load`) |>
  ggplot(aes(
    x = site,
    y = coverage,
    fill = as.character(Viral.load)
  )) +
  geom_col() +
  facet_grid(seg ~ Sample_id) +
  ylab("Coverage") +
  ggtitle("Influenza B virus (Background 1 deduplicated)") +
  guides(fill = guide_legend(title = "Viral load")) +
 theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10() +
  scale_fill_manual(values = cols4, label = c(expression("10"^"2"), expression("10"^"3"), expression("10"^"5")))

FLU_ME2 <- persite_norm |>
  filter(virus == "Influenza_B_virus") |>
  filter(type == "dedup_TE") |>
  filter(Background == "p2") |>
  rename(Viral.load = `Viral load`) |>
  ggplot(aes(
    x = site,
    y = coverage,
    fill = as.character(Viral.load)
  )) +
  geom_col() +
  facet_grid(seg ~ Sample_id) +
  ylab("Coverage") +
  ggtitle("Influenza B virus (Background 2 deduplicated)") +
  guides(fill = guide_legend(title = "Viral load")) +
 theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10() +
  scale_fill_manual(values = cols4, label = c(expression("10"^"2"), expression("10"^"3"), expression("10"^"5")))

@@

####***Final plot***
```{r}

ggsave("figures/manuscript_figure_2025/PDF/Figure_S8.pdf",
       width=20,
       height=12,
       dpi=600)

ggsave("figures/manuscript_figure_2025/PNG/Figure_S8.png",
       width=20,
       height=12)
```

@@

### Figure S9
```{r}

REO_ME1 <- 
  persite_norm |>
  filter(virus == "Mammalian_orthoreovirus3") |>
  filter(type == "dedup_TE") |>
  filter(Background == "p2") |>
  rename(Viral.load = `Viral load`) |>
  ggplot(aes(
    x = site,
    y = coverage,
    fill = as.character(Viral.load)
  )) +
  geom_col() +
  facet_grid(seg ~ Sample_id) +
  ylab("log10(Coverage)") +
  ggtitle("Mammalian orthoreovirus 3 (Background 1 deduplicated)") +
  guides(fill = guide_legend(title = "Viral load")) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top",
    panel.grid.major = element_line(linewidth = 0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth = 0.1, color = "lightgray")
  ) +
  scale_y_log10() +
  scale_fill_manual(values = cols4,
                    label = c(
                      expression("10" ^ "2"),
                      expression("10" ^ "3"),
                      expression("10" ^ "5")
                    ))

REO_ME2 <- 
  persite_norm |>
  filter(virus == "Mammalian_orthoreovirus3") |>
  filter(type == "dedup_TE") |>
  filter(Background == "p8") |>
  rename(Viral.load = `Viral load`) |>
  ggplot(aes(
    x = site,
    y = coverage,
    fill = as.character(Viral.load)
  )) +
  geom_col() +
  facet_grid(seg ~ Sample_id) +
  ylab("log10(Coverage)") +
  ggtitle("Mammalian orthoreovirus 3 (Background 2 deduplicated)") +
  guides(fill = guide_legend(title = "Viral load")) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top",
    panel.grid.major = element_line(linewidth = 0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth = 0.1, color = "lightgray")
  ) + scale_y_log10() +
  scale_fill_manual(values = cols4,
                    label = c(
                      expression("10" ^ "2"),
                      expression("10" ^ "3"),
                      expression("10" ^ "5")
                    ))

@@

@@

####***Final plot***
```{r}
ggsave("figures/manuscript_figure_2025/PDF/Figure_S9.pdf",
       width=20,
       height=12,
       dpi=600)

ggsave("figures/manuscript_figure_2025/PNG/Figure_S9.png",
       width=20,
       height=12,
       dpi=600)
```
